---
title: "p8105_hw5_iho2104"
author: "Ixtaccihuatl Obregon"
date: "`r Sys.Date()`"
output: github_document
---

```{r}
library(tidyverse)
library(dplyr)
library(purrr)
library(ggplot2)
library(broom)
```

## Problem One

```{r}

```

## Problem Two

```{r}
## CON
file_paths_c = list.files("data", pattern = "con_\\d+\\.csv", full.names = TRUE)
controls = map_dfr(file_paths_c, read.csv) |> 
  mutate(id = c("con_01", "con_02", "con_03", "con_04", "con_05", "con_06", "con_07", "con_08", "con_09", "con_10" )) |> 
  select(id, everything()) 

## EXP
file_paths_e = list.files("data", pattern = "exp_\\d+\\.csv", full.names = TRUE)
exp = map_dfr(file_paths_e, read.csv) |> 
  mutate(id = c("exp_01", "exp_02", "exp_03", "exp_04", "exp_05", "exp_06", "exp_07", "exp_08", "exp_09", "exp_10" )) |> 
  select(id, everything()) 

# combined arms 
df = rbind(controls, exp) |> 
  separate(col = id, into = c("arm", "id"), sep = "_") |> 
  pivot_longer(cols = starts_with("week"), names_to = "week", values_to = "value") 

df_plot = df |> 
  mutate(sub_id = paste(arm, id, sep = "_"))

# spaghetti plot 
df_plot |> 
  ggplot(aes(x = week, y = value, group = sub_id, color = arm)) +
  geom_line() +
  labs(title = "Spaghetti Plot", x = "Time", y = "Value")
```

## Problem Three

Following chunk attempted to integrate a for loop and function to obtain 3500 observations consisting of variables: mu, iteration, estimate, and p.value. 

```{r, eval= FALSE}
fix_n = 30 
fix_sigma = 5 
mu_val= c(0,1,2,3,4,5,6)
datasets = vector("list", length = 5000)

for (i in 1:5000) {
  dataset = rnorm(fix_n, mean = mu_val, sd = fix_sigma) # Generate a dataset
  t_test_results = lapply(mu_val, function(mu) {      # Function
  t_test_result = t.test(dataset, mu = mu)            # Perform t-test
  tidy_result = tidy(t_test_result)                   # Extract estimates and p-value 
  tibble::tibble(estimate = tidy_result$estimate[1],  # Assuming one-sided t-test
                   p_value = tidy_result$p.value[1])  # Assuming one-sided t-test
})
  
datasets[[i]] = do.call(rbind, t_test_results) 
}

results_df = do.call(rbind, datasets)
results_df = mutate(results_df, estimate = sub("sub_str", "", estimate)) |> 
select(estimate, p_value)
head(results_df)
```

I used the for-loop 7 times to generate my dataframe with 35000 obs and 4 variables. 

```{r}
#mu_val = 0 
fix_n = 30
fix_sigma = 5
mu = 0
datasets <- vector("list", length = 5000)

for (i in 1:5000) {
  dataset = rnorm(fix_n, mean = mu, sd = fix_sigma)
  t_test_result = t.test(dataset, mu = mu)
  tidy_result = broom::tidy(t_test_result)
  datasets[[i]] = tibble::tibble(
    mu = mu, 
    iteration = i, 
    estimate = tidy_result$estimate[1],
    p_value = tidy_result$p.value[1])
}


results_df_0 = do.call(rbind, datasets)


results_df_0 = mutate(results_df_0, estimate = sub("sub_str", "", estimate))  # Remove sub_str from estimate
results_df_0 = results_df_0 |> 
  select(mu, iteration,estimate, p_value)

head(results_df_0)
```

```{r}
#mu_val = 1
fix_n = 30
fix_sigma = 5
mu = 1
datasets <- vector("list", length = 5000)

for (i in 1:5000) {
  dataset = rnorm(fix_n, mean = mu, sd = fix_sigma)
  t_test_result = t.test(dataset, mu = mu)
  tidy_result = broom::tidy(t_test_result)
  datasets[[i]] = tibble::tibble(
    mu = mu, 
    iteration = i, 
    estimate = tidy_result$estimate[1],
    p_value = tidy_result$p.value[1])
}

results_df_1 = do.call(rbind, datasets)
results_df_1 = mutate(results_df_1, estimate = sub("sub_str", "", estimate))
results_df_1 = results_df_1 |> 
  select(mu, iteration,estimate, p_value)

head(results_df_1)
```

```{r}
#mu_val = 2
fix_n = 30
fix_sigma = 5
mu = 2
datasets <- vector("list", length = 5000)

for (i in 1:5000) {
  dataset = rnorm(fix_n, mean = mu, sd = fix_sigma)
  t_test_result = t.test(dataset, mu = mu)
  tidy_result = broom::tidy(t_test_result)
  datasets[[i]] = tibble::tibble(
    mu = mu, 
    iteration = i, 
    estimate = tidy_result$estimate[1],
    p_value = tidy_result$p.value[1])
}

results_df_2 = do.call(rbind, datasets)
results_df_2 = mutate(results_df_2, estimate = sub("sub_str", "", estimate))
results_df_2 = results_df_2 |> 
  select(mu, iteration,estimate, p_value)

head(results_df_2)
```


```{r}
#mu_val = 3
fix_n = 30
fix_sigma = 5
mu = 3
datasets <- vector("list", length = 5000)

for (i in 1:5000) {
  dataset = rnorm(fix_n, mean = mu, sd = fix_sigma)
  t_test_result = t.test(dataset, mu = mu)
  tidy_result = broom::tidy(t_test_result)
  datasets[[i]] = tibble::tibble(
    mu = mu, 
    iteration = i, 
    estimate = tidy_result$estimate[1],
    p_value = tidy_result$p.value[1])
}

results_df_3 = do.call(rbind, datasets)
results_df_3 = mutate(results_df_3, estimate = sub("sub_str", "", estimate))
results_df_3 = results_df_3 |> 
  select(mu, iteration,estimate, p_value)

head(results_df_3)
```

```{r}
#mu_val = 4
fix_n = 30
fix_sigma = 5
mu = 4
datasets <- vector("list", length = 5000)

for (i in 1:5000) {
  dataset = rnorm(fix_n, mean = mu, sd = fix_sigma)
  t_test_result = t.test(dataset, mu = mu)
  tidy_result = broom::tidy(t_test_result)
  datasets[[i]] = tibble::tibble(
    mu = mu, 
    iteration = i, 
    estimate = tidy_result$estimate[1],
    p_value = tidy_result$p.value[1])
}

results_df_4 = do.call(rbind, datasets)
results_df_4 = mutate(results_df_4, estimate = sub("sub_str", "", estimate))
results_df_4 = results_df_4 |> 
  select(mu, iteration,estimate, p_value)

head(results_df_4)

```

```{r}
#mu_val = 5
fix_n = 30
fix_sigma = 5
mu = 5
datasets <- vector("list", length = 5000)

for (i in 1:5000) {
  dataset = rnorm(fix_n, mean = mu, sd = fix_sigma)
  t_test_result = t.test(dataset, mu = mu)
  tidy_result = broom::tidy(t_test_result)
  datasets[[i]] = tibble::tibble(
    mu = mu, 
    iteration = i, 
    estimate = tidy_result$estimate[1],
    p_value = tidy_result$p.value[1])
}

results_df_5 = do.call(rbind, datasets)
results_df_5 = mutate(results_df_5, estimate = sub("sub_str", "", estimate))
results_df_5 = results_df_5 |> 
  select(mu, iteration,estimate, p_value)

head(results_df_5)
```

```{r}
#mu_val = 6
fix_n = 30
fix_sigma = 5
mu = 6
datasets <- vector("list", length = 5000)

for (i in 1:5000) {
  dataset = rnorm(fix_n, mean = mu, sd = fix_sigma)
  t_test_result = t.test(dataset, mu = mu)
  tidy_result = broom::tidy(t_test_result)
  datasets[[i]] = tibble::tibble(
    mu = mu, 
    iteration = i, 
    estimate = tidy_result$estimate[1],
    p_value = tidy_result$p.value[1])
}

results_df_6 = do.call(rbind, datasets)
results_df_6 = mutate(results_df_6, estimate = sub("sub_str", "", estimate))
results_df_1 = results_df_6 |> 
  select(mu, iteration,estimate, p_value)

head(results_df_6)
```
```{r}
combined_results = rbind(results_df_0, results_df_1, results_df_2, results_df_3, results_df_4, results_df_5, results_df_6)
```


Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.

```{r}

```



